Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-20 wearables_survey.tex
rough conclusion done.

\section{Conclusion}
END STRONG! Echo the conclusion a little, remind the people of the takeaways in a way that highlights the contribution of this paper.

>>>>

\section{Conclusion}
(REDO) END STRONG! Should I put this before the Discussion?  Echo the introduction a little, remind the people of the takeaways in a way that highlights the contribution of this paper. Intro: ``we studied user perceptions for threats in wearable devices, along with user perceptions of risk and benefit for emerging technologies and what they thought was the biggest risk for using wearable devices. Data type, data recipient, and device type all matter different amounts. All new technologies were perceived to be low risk low benefit but we think this is because people are unfamiliar with these technologies. Privacy was the number one concern, followed by security, then health, money, social norms changing and social stigma. Fantastic ending sentence here.''

I can talk about the results a little bit more in depth because people have already supposedly read my whole paper now. Pull out the subtleties I couldn't have done in the introduction, and go into specific details, shooting out numbers and statistics. Then conclude the whole thing with an inspirational pitch on how there is much future work to be done in this area, how this area is exciting, and how I basically helped people see both of these things.
